State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
solving conflict
corrected the typo in table1
added smoother to the matlab implementation
Visakan comments on conclusion, last paragraph

%\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}

@@

\section{Results}\label{ResultsSection} The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology. This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation. The Mexican hat connectivity kernel is typically comprised of 2 Gaussian basis functions. Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

	$\tau$ & 0.01 & ms$^{-1}$\\

@@

In this paper, the widths of the connectivity kernel basis functions are assumed to be known. In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths. We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure take care of the weights. In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions. For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas. In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria. Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.

>>>>

% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, NY, USA} \address{$^4$ Department of Systems and Control Engineering, University of Malta, Msida, MSD 1333, Malta} \address{$^5$ The Bionic Ear Institute, East Melbourne, VIC 3002Australia} \ead{dfreestone@bionicear.org}

@@

\section{Results}\label{ResultsSection} The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Note, the parameters for the spatial and temporal aspects of the model can be considered arbitrary when demonstrating the estimation methodology. This is due to the fact that the temporal aspects scale with the sampling rate and the length of the times series and the spatial aspects scale with the size of the neural field and the space step used for numerical simulation. Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

	$\tau$ & 0.01 & s$^{-1}$\\

@@

In this paper,\parham{In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel. In future work, we plan to extent this work to relax this assumption. We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions. Visakan: width estimation is totally different process} the widths of the connectivity kernel basis functions are assumed to be known. In future work, we plan to extend this work to estimate the connectivity structure with unknown kernel basis function widths. We hope to achieve this by using a sufficiently large set of connectivity basis functions within the physiological plausible limits, and allow the estimation procedure take care of the weights. In addition, we plan to show in future work how the assumption of homogeneity can be relaxed, where heterogeneity can be modelled by careful placement of field basis functions. For example, if cortical regions have a greater density of neural populations, then more basis functions can be used in these areas \parham{Visakan: heteroginity is about the process not presentation, and it should be addressed by using a kernel which is different at different spatial locations}. In this scenario, model selection and basis function positioning can be achieved using instantaneous frequency analysis of the the neural field or alternative model selection tools based on information criteria. Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.
